### 2012-02-10 docs/SDC/sdc.tex
my guess at I_{X_k}

>>>>

(Andy's Idea) Define $I_{X_k}$ using
\begin{equation}
I_{X_k} = \frac{X_k^\mathrm{new} - X_k^\mathrm{old}}{\Delta t} - A_{X_k},
\end{equation}
where we first define a state that has only been updated with advection:
\begin{equation}
\frac{(\rho X_k)^{(1)} - (\rho X_k)^\mathrm{old}}{\Delta t} = A_{\rho X_k},
\end{equation}
and then define the species mass fractions,
\begin{equation}
X_k^{(1)} = (\rho X_k)^{(1)} / \sum_k (\rho X_k)^{(1)}, \quad 
X_k^\mathrm{old} = (\rho X_k)^\mathrm{old} / \sum_k (\rho X_k)^\mathrm{old}, \quad 
X_k^\mathrm{new} = (\rho X_k)^\mathrm{new} / \sum_k (\rho X_k)^\mathrm{new},
\end{equation}
and finally define $A_{X_k}$ using
\begin{equation}
\frac{X^{(1)} - X^\mathrm{old}}{\Delta t}= A_{X_k}.
\end{equation}
